Simulations of Ballot Polling Risk-Limiting Audits

### 2022-01-11 MultipleRoundSims/draft.tex
minor edits

\begin{document}
\lstset{language=Python}
%
\title{Simulations of Ballot Polling Risk-Limiting Audits}
%add \thanks{} within the title brackets if want to refer to supporting organization ^^
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\begin{comment}
\author{Oliver Broadrick\inst{1} \and
Sarah Morin\inst{1} \and
Grant McClearn\inst{2} \and Neal McBurnett \and Poorvi L. Vora\inst{1} \and
Filip Zag{\'o}rski\inst{3} }
%
\authorrunning{Broadrick, Morin et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Department of Computer Science, The George Washington University 
\email{obroadrick@gwmail.gwu.edu}\\
\and
Department of Computer Science, Stanford University 
\email{grantmcc@stanford.edu}\\
\and Wroclaw University of Science and Technology\\
\email{filip.zagorski@gmail.com}}
%
\end{comment}
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    In this paper we present simulation results comparing the risk, stopping probability, and number of ballots required over multiple rounds of ballot polling risk-limiting audits (RLAs) \Minerva, Selection-Ordered (SO) \BRAVO, and End-of-Round (EoR) \BRAVO.    
    \BRAVO is the most commonly used ballot polling RLA and requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announced. 
    In real audits, multiple ballots are drawn at a time, and \BRAVO is implemented as SO \BRAVO or EoR \BRAVO. 
    \Minerva is a recently proposed ballot polling RLA that requires fewer ballots than either implementation of \BRAVO in the first round but requires a predetermined round schedule.
    %\BRAVO is the most commonly used ballot polling RLA and requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announced. In real audits, election officials draw multiple ballots at a time, and \BRAVO rules may be implemented as SO \BRAVO or EoR \BRAVO, with neither being optimal for large first round sizes. \Minerva was recently proposed for use when the first-round stopping probability is large. It requires fewer first-round ballots, on average, than both SO \BRAVO and EoR \BRAVO for first round stopping probabilities of $0.9$ when the (true) underlying election is as announced. 
    It is an open question how these audits compare over multiple rounds and for lower stopping probabilities. 
    Our simulations use stopping probabilities of $0.9$ and $0.25$.
    %In this paper, we present results from simulations of multiple round audits with stopping probabilities of $0.9$ and $0.25$.
    %We examine both: first-round stopping probabilities of $0.9$, a common choice among election officials, and $0.25$, which would be more favorable to \BRAVO. 
    The results are consistent with predictions of the R2B2 open-source library for ballot polling audits. 
    %Because the \Minerva round schedule needs to be predetermined, we observe that the simulator is useful as a tool for understanding the behavior of \Minerva with the fixed round schedule. 
    We observe that both \BRAVO audits are more conservative than \Minerva, which stops with fewer ballots, for both first round stopping probabilities. 
    However, the advantage of using \Minerva decreases considerably for the smaller first round stopping probability, as one would expect.

>>>>

\begin{document}
\lstset{language=Python}
%
\title{Simulations of Ballot Polling Risk-Limiting Audits}
%add \thanks{} within the title brackets if want to refer to supporting organization ^^
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\begin{comment}
\author{Oliver Broadrick\inst{1} \and
Sarah Morin\inst{1} \and
Grant McClearn\inst{2} \and Neal McBurnett \and Poorvi L. Vora\inst{1} \and
Filip Zag{\'o}rski\inst{3} }
%
\authorrunning{Broadrick, Morin et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Department of Computer Science, The George Washington University 
\email{obroadrick@gwmail.gwu.edu}\\
\and
Department of Computer Science, Stanford University 
\email{grantmcc@stanford.edu}\\
\and Wroclaw University of Science and Technology\\
\email{filip.zagorski@gmail.com}}
%
\end{comment}
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    In this paper we present simulation results comparing the risk, stopping probability, and number of ballots required over multiple rounds of ballot polling risk-limiting audits (RLAs) \Minerva, Selection-Ordered (SO) \BRAVO, and End-of-Round (EoR) \BRAVO.    
    \BRAVO is the most commonly used ballot polling RLA and requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announc/for ed. 
    In real audits, multiple ballots are drawn at a time, and \BRAVO is implemented as SO \BRAVO or EoR \BRAVO. 
    \Minerva is a recently proposed ballot polling RLA that requires fewer ballots than either implementation of \BRAVO in a first round with stopping probability $0.9$ but requires a predetermined round schedule.
    %\BRAVO is the most commonly used ballot polling RLA and requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announced. In real audits, election officials draw multiple ballots at a time, and \BRAVO rules may be implemented as SO \BRAVO or EoR \BRAVO, with neither being optimal for large first round sizes. \Minerva was recently proposed for use when the first-round stopping probability is large. It requires fewer first-round ballots, on average, than both SO \BRAVO and EoR \BRAVO for first round stopping probabilities of $0.9$ when the (true) underlying election is as announced. 
    It is an open question how these audits compare over multiple rounds and for lower stopping probabilities. 
    Our simulations use stopping probabilities of $0.9$ and $0.25$.
    %In this paper, we present results from simulations of multiple round audits with stopping probabilities of $0.9$ and $0.25$.
    %We examine both: first-round stopping probabilities of $0.9$, a common choice among election officials, and $0.25$, which would be more favorable to \BRAVO. 
    The results are consistent with predictions of the R2B2 open-source library for ballot polling audits. 
    %Because the \Minerva round schedule needs to be predetermined, we observe that the simulator is useful as a tool for understanding the behavior of \Minerva with the fixed round schedule. 
    We observe that both \BRAVO audits are more conservative than \Minerva, which stops with fewer ballots, for both first round stopping probabilities. 
    However, the advantage of using \Minerva decreases considerably for the smaller first round stopping probability, as one would expect.

### 2022-01-11 MultipleRoundSims/sections/02-related.tex
minor edits

%Related Work
The \BRAVO audit \cite{bravo} is a well-known ballot polling audit which has been used in numerous pilot and real audits. When used to audit a two-candidate election, it is an instance of Wald's sequential probability ratio test (SPRT) \cite{wald}, and inherits the SPRT property of being the most efficient test (requiring the smallest expected number of ballots) if the election is as announced. The model for \BRAVO and the SPRT is, however, that of a sequential audit: a sample of size one is drawn, and a decision of whether to stop the audit or not is taken. Real election audits invest in drawing large numbers of ballot, called rounds, before making stopping decisions because sequentially sampling individual ballots has significant overhead (unsealing and searching for specific ballots). It is possible to apply \BRAVO to the sequence of ballots in a round if the sequential order is retained. This is not, however, the most efficient possible use of the drawn sample because information in consequent ballots is ignored when applying \BRAVO to ballots that were drawn earlier in the sample.

@@

The \Minerva audit \cite{usenix_minerva,arxiv_athena} was developed for large first round sizes which enable election officials to be done in one round with large probability. It uses information from the entire sample, and has been proven to be risk limiting when the round schedule for the audit is determined before the audit begins. That is, information about the actual ballots drawn in the first round cannot be used to determine future round sizes. First-round sizes for a $0.9$ stopping probability when the election is as announced have been computed for a wide range of margins and shown to be smaller than those for both EoR and SO \BRAVO. First round simulations of \Minerva \cite{arxiv_athena} demonstrate that its first-round properties---regarding the probabilities of stopping when the underlying election is tied and when it is as announced---are as predicted for first round sizes with stopping probability $0.9$.

Ballot polling audit simulations have been used to familiarize election officials and the public with the approach \cite{dice}. McLaughlin and Stark \cite{mclaughlin_thesis,simulations_house} compare the workload for the Canvass Audits by Sampling and Testing (CAST) and Kaplan-Markov (KM) audits using simulations. Blom {\em et al.} demonstrate the efficiency of their ballot polling approach to audit instant runoff voting (IRV) using simulations \cite{blom_IRV}. Huang {\em et al.} present a framework generalizing a number of ballot polling audits and compare their performance (round sizes and stopping probabilities) using simulations \cite{DBLP:conf/evoteid/HuangRSTV20}. This work was prior to the development of \Minerva, and focuses on the comparison between Bayesian audits \cite{bayesian-audits} and \BRAVO, essentially studying the impact of the prior of the Bayesian RLA. Some workload measurements have been made\cite{RI-report}. While workload can be estimated with simple metrics like number of ballots examined\cite{bernoulli-ballot-polling}, Bernhard presents a more complex workload estimation model\cite{bernhard-diss}.

>>>>

%Related Work
The \BRAVO audit \cite{bravo} is a well-known ballot polling audit which has been used in numerous pilot and real audits. When used to audit a two-candidate election, it is an instance of Wald's sequential probability ratio test (SPRT) \cite{wald}, and inherits the SPRT property of being the most efficient test (requiring the smallest expected number of ballots) if the election is as announced. The model for \BRAVO and the SPRT is, however, that of a sequential audit: a sample of size one is drawn, and a decision of whether to stop the audit or not is taken. Real election audits invest in drawing large numbers of ballot, called rounds, before making stopping decisions because sequentially sampling individual ballots has significant overhead (unsealing and searching for individual ballots). It is possible to apply \BRAVO to the sequence of ballots in a round if the sequential order is retained. This is not, however, the most efficient possible use of the drawn sample because information in consequent ballots is ignored when applying \BRAVO to ballots that were drawn earlier in the sample.

@@

The \Minerva audit \cite{usenix_minerva,arxiv_athena} was developed for large first round sizes which enable election officials to be done in one round with large probability. It uses information from the entire sample, and has been proven to be risk limiting when the round schedule for the audit is determined before the audit begins. That is, information about the actual ballots drawn in the first round cannot inform future round sizes. First-round sizes for a $0.9$ stopping probability when the election is as announced have been computed for a wide range of margins and are smaller than those for EoR and SO \BRAVO. First round simulations of \Minerva \cite{arxiv_athena} demonstrate that its first-round properties---regarding the probabilities of stopping when the underlying election is tied and when it is as announced---are as predicted for first round sizes with stopping probability $0.9$.

Ballot polling audit simulations have been used to familiarize election officials and the public with the approach \cite{dice}. McLaughlin and Stark \cite{mclaughlin_thesis,simulations_house} compare the workload for the Canvass Audits by Sampling and Testing (CAST) and Kaplan-Markov (KM) audits using simulations. Blom {\em et al.} demonstrate the efficiency of their ballot polling approach to audit instant runoff voting (IRV) using simulations \cite{blom_IRV}. Huang {\em et al.} present a framework generalizing a number of ballot polling audits and compare their performance (round sizes and stopping probabilities) using simulations \cite{DBLP:conf/evoteid/HuangRSTV20}. This work was prior to the development of \Minerva, and focuses on the comparison between Bayesian audits \cite{bayesian-audits} and \BRAVO, essentially studying the impact of the prior of the Bayesian RLA. Some workload measurements have been made\cite{RI-report}. While total ballots sampled can give naive workload estimates\cite{bernoulli-ballot-polling}, Bernhard presents a more complex workload estimation model\cite{bernhard-diss}.
